19Q2

### 2019-07-19 19Q2.Rmd
update w/ new lineage tests and CRISPR merge/tests

```{r g2p}
g2p <- read.delim("./data_munging/g2p_db_edited_20190718.csv", sep = ",", header = TRUE, row.names = 1)
g2p$Drug_Gene_Lin <- gsub(pattern = " cancer", "", g2p$Drug_Gene_Lin)

@@

g2p$biomarker_type_curated <- ifelse(is.na(g2p$biomarker_type_curated), "None", as.character(g2p$biomarker_type_curated))
g2p_split <- filter(g2p, !is.na(Drug)) %>% group_split(biomarker_type_curated)
g2p_amp <- g2p_split[[1]]
g2p_expr <- g2p_split[[2]]
g2p_fus <- g2p_split[[3]]
g2p_fus$FusionPair <- sapply(X = g2p_fus$Feature.Names, function(x) strsplit(as.character(x)," ")[[1]][1])
g2p_fus$FusionPair <- ifelse(g2p_fus$FusionPair == "Fusions", as.character(g2p_fus$Gene), as.character(g2p_fus$FusionPair))
g2p_fus$FusionPair <- ifelse(g2p_fus$FusionPair == "BCR-ABL", "BCR-ABL1", as.character(g2p_fus$FusionPair))
g2p_fus$Drug_FusionPair <- ifelse(is.na(g2p_fus$Drug) | is.na(g2p_fus$FusionPair), NA, paste0(g2p_fus$Drug, "_", g2p_fus$FusionPair))
g2p_mut <- g2p_split[[4]] %>% drop_na(Direction_Curated)
g2p_mut_genes <- unique(sapply(strsplit(as.character(g2p_mut$Drug_Gene)[!is.na(g2p_mut$Drug_Gene)], "_", fixed = TRUE), function(x) x[2]))

g2p_prot <- unique(filter(g2p, !is.na(Gene_Protein_Change) & !is.na(Drug)) %>% select(disease, Drug, Direction_Curated, Gene, Protein_Change, Gene_Protein_Change))
```

@@

    grid <- expand.grid("Cell_line" = unique(dataframe$Cell_line), "Gene" = gene_list)
    data <-  merge(dataframe, grid, by = "Cell_line", all.y = TRUE)
    print("Merged grid.")
    # Merge metadata
    data <-  merge(data, ccl_meta, by = "DepMap_ID", all.y = TRUE)
    ## Add columns for G2P drug-gene and drug-gene-lineage sorting
    data$Drug_Gene <- paste0(data$Drug, "_", data$Gene)
    data$G2P_Drug_Gene <- ifelse(data$Drug_Gene %in% g2p_dg, "Yes", "No")
    data$Drug_Gene_Lin <- paste0(data$Drug, "_", data$Gene, "_", data$disease)
    data$G2P_Drug_Gene_Lin <- ifelse(data$Drug_Gene_Lin %in% g2p_dgl, "Yes", "No")
    print("Merged metadata.")
    # Merge mutation calls
    data <- unfactorize(data)
    data <- merge(data, maf_df, by = c("Gene", "DepMap_ID"), all.x = TRUE)
    data$Mutation <- ifelse(is.na(data$Mutation), 0, data$Mutation)
  }
  if(database == "CRISPR") {
    print(paste0("Processing ", database, " data."))
    # Melt CRISPR dataset for merging
    data <- melt(dataframe, id.vars = "DepMap_ID", measure.vars = colnames(crispr_all)[2:ncol(crispr_all)], variable.name = "Gene", value.name = "Score")
    # Merge cell line metadata
    data <- merge(data, ccl_meta, by = "DepMap_ID", all.y = TRUE)
    print("Merged metadata.")
    # Merge mutation calls
    data <- unfactorize(data)
    data <- merge(data, maf_df, by = c("Gene", "DepMap_ID"), all.x = TRUE)
    data$Mutation <- ifelse(is.na(data$Mutation), 0, data$Mutation)
  }

@@

`r nrow(filter(test, n != 1))`/`r nrow(test)` gene-cell line combinations have more than one mutation in the MAF file. This is corrected in the point mutation filtering done below.
```{r merge_drug_data, eval=FALSE}
ccle_all <- readRDS("./../htscreens_giant_files/pozdeyev_data/pozdeyev2016_ccle_all_edited.rds")
ctrp_all <- readRDS("./../htscreens_giant_files/pozdeyev_data/pozdeyev2016_ctrp_all_edited.rds")
gdsc_all <- readRDS("./../htscreens_giant_files/pozdeyev_data/pozdeyev2016_gdsc_all_edited.rds")

ccle <- MergeOmicsG2P(database = "CCLE", dataframe = ccle_all, maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./data_munging/19Q2/ccle_data_19Q2.rds")
# write.csv.gz(ccle %>% drop_na(Score), "./data_munging/19Q2/ccle_data_19Q2.csv.gz")

ctrp <- MergeOmicsG2P(database = "CTRP", dataframe = ctrp_all, maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./../htscreens_giant_files/ctrp_data_19Q2.rds")
# write.csv.gz(ctrp %>% drop_na(Score), "./../htscreens_giant_files/ctrp_data_19Q2.csv.gz")

gdsc <- MergeOmicsG2P(database = "GDSC", dataframe = gdsc_all, maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./data_munging/19Q2/gdsc_data_19Q2.rds")
# write.csv.gz(gdsc %>% drop_na(Score), "./../htscreens_giant_files/gdsc_data_19Q2.csv.gz")

# all_genes <- intersect(unique(maf_df$Gene), intersect(unique(cn_melt$Gene), unique(ge_melt$Gene)))
# ccle <- MergeOmicsG2P(database = "CCLE", maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = all_genes, outfile = "./../htscreens_giant_files/ccle_data_allgenes_19Q2.rds")
# ctrp <- MergeOmicsG2P(database = "CTRP", maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = all_genes, outfile = "./../htscreens_giant_files/ctrp_data_allgenes_19Q2.rds")
# gdsc <- MergeOmicsG2P(database = "GDSC", maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = all_genes, outfile = "./../htscreens_giant_files/gdsc_data_allgenes_19Q2.rds")
```

@@

ccle_fus_grid <- expand.grid("DepMap_ID" = unique(ccle_all$DepMap_ID), "FusionPair" = unique(fusions_filt$FusionPair))
ccle_fus <- merge(merge(ccle_all, ccle_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "CCLE_name", "CCLE_histology", "Cell_line", "FusionPair"), all = TRUE)
ccle_fus$Fusion_Status <- ifelse(!is.na(ccle_fus$LeftGene), "Yes", "No")
ccle_fus$Drug_FusionPair <- ifelse(is.na(ccle_fus$Drug) | is.na(ccle_fus$FusionPair), NA, paste0(ccle_fus$Drug, "_", ccle_fus$FusionPair))
ccle_fus$G2P_Drug_FusionPair <- ifelse(ccle_fus$Drug_FusionPair %in% unique(as.character(g2p_fus$Drug_FusionPair)), "Yes", "No")
ccle_fus$G2P_Fusion <- ifelse(ccle_fus$FusionPair %in% unique(as.character(g2p_fus$FusionPair)), "Yes", "No")
ccle_fus$Database <- "CCLE"

ctrp_fus_grid <- expand.grid("DepMap_ID" = unique(ctrp_all$DepMap_ID), "FusionPair" = unique(fusions_filt$FusionPair))
ctrp_fus <- merge(merge(ctrp_all, ctrp_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "CCLE_name", "CCLE_histology", "Cell_line", "FusionPair"), all = TRUE)
ctrp_fus$Fusion_Status <- ifelse(!is.na(ctrp_fus$LeftGene), "Yes", "No")
ctrp_fus$Drug_FusionPair <- ifelse(is.na(ctrp_fus$Drug) | is.na(ctrp_fus$FusionPair), NA, paste0(ctrp_fus$Drug, "_", ctrp_fus$FusionPair))
ctrp_fus$G2P_Drug_FusionPair <- ifelse(ctrp_fus$Drug_FusionPair %in% unique(as.character(g2p_fus$Drug_FusionPair)), "Yes", "No")
ctrp_fus$G2P_Fusion <- ifelse(ctrp_fus$FusionPair %in% unique(as.character(g2p_fus$FusionPair)), "Yes", "No")
ctrp_fus$Database <- "CTRP"

gdsc_fus_grid <- expand.grid("DepMap_ID" = unique(gdsc_all$DepMap_ID), "FusionPair" = unique(fusions_filt$FusionPair))
gdsc_fus <- merge(merge(gdsc_all, gdsc_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "CCLE_name", "CCLE_histology", "Cell_line", "FusionPair"), all = TRUE)
gdsc_fus$Fusion_Status <- ifelse(!is.na(gdsc_fus$LeftGene), "Yes", "No")
gdsc_fus$Drug_FusionPair <- ifelse(is.na(gdsc_fus$Drug) | is.na(gdsc_fus$FusionPair), NA, paste0(gdsc_fus$Drug, "_", gdsc_fus$FusionPair))
gdsc_fus$G2P_Drug_FusionPair <- ifelse(gdsc_fus$Drug_FusionPair %in% unique(as.character(g2p_fus$Drug_FusionPair)), "Yes", "No")
gdsc_fus$G2P_Fusion <- ifelse(gdsc_fus$FusionPair %in% unique(as.character(g2p_fus$FusionPair)), "Yes", "No")
gdsc_fus$Database <- "GDSC"

@@

# CCLE
ccle_prot_grid <- expand.grid("DepMap_ID" = unique(ccle_all$DepMap_ID), "Gene_Protein_Change" = unique(maf_changes_filt$Gene_Protein_Change))
ccle_prot <- merge(ccle_all, ccle_prot_grid, by = "DepMap_ID", all = TRUE)
ccle_prot <- merge(ccle_prot, maf_changes_filt, by = c("DepMap_ID", "Gene_Protein_Change"), all = TRUE)
ccle_prot$Change_Status <- ifelse(!is.na(ccle_prot$Protein_Change), "Yes", "No")
ccle_prot$Drug_Gene_Protein_Change <- ifelse(is.na(ccle_prot$Drug) | is.na(ccle_prot$Gene_Protein_Change), NA, paste0(ccle_prot$Drug, "_", ccle_prot$Gene_Protein_Change))
ccle_prot$G2P_Drug_Gene_Protein_Change <- ifelse(ccle_prot$Drug_Gene_Protein_Change %in% unique(as.character(g2p_prot$Drug_Gene_Protein_Change)), "Yes", "No")
ccle_prot$G2P_Protein_Change <- ifelse(ccle_prot$Gene_Protein_Change %in% unique(as.character(g2p_prot$Gene_Protein_Change)), "Yes", "No")
ccle_prot <- merge(ccle_prot, unique(select(g2p_prot, Drug_Gene_Protein_Change, Direction_Curated)), by = "Drug_Gene_Protein_Change", all.x = TRUE)
ccle_prot$Database <- "CCLE"
ccle_prot <- ccle_prot %>% drop_na(Drug)

# CTRP
ctrp_prot_grid <- expand.grid("DepMap_ID" = unique(ctrp_all$DepMap_ID), "Gene_Protein_Change" = unique(maf_changes_filt$Gene_Protein_Change))
ctrp_prot <- merge(ctrp_all, ctrp_prot_grid, by = "DepMap_ID", all = TRUE)
ctrp_prot <- merge(ctrp_prot, maf_changes_filt, by = c("DepMap_ID", "Gene_Protein_Change"), all = TRUE)
ctrp_prot$Change_Status <- ifelse(!is.na(ctrp_prot$Protein_Change), "Yes", "No")
ctrp_prot$Drug_Gene_Protein_Change <- ifelse(is.na(ctrp_prot$Drug) | is.na(ctrp_prot$Gene_Protein_Change), NA, paste0(ctrp_prot$Drug, "_", ctrp_prot$Gene_Protein_Change))
ctrp_prot$G2P_Drug_Gene_Protein_Change <- ifelse(ctrp_prot$Drug_Gene_Protein_Change %in% unique(as.character(g2p_prot$Drug_Gene_Protein_Change)), "Yes", "No")
ctrp_prot$G2P_Protein_Change <- ifelse(ctrp_prot$Gene_Protein_Change %in% unique(as.character(g2p_prot$Gene_Protein_Change)), "Yes", "No")
ctrp_prot <- merge(ctrp_prot, unique(select(g2p_prot, Drug_Gene_Protein_Change, Direction_Curated)), by = "Drug_Gene_Protein_Change", all.x = TRUE)
ctrp_prot$Database <- "CTRP"
ctrp_prot <- ctrp_prot %>% drop_na(Drug)

# GDSC
gdsc_prot_grid <- expand.grid("DepMap_ID" = unique(gdsc_all$DepMap_ID), "Gene_Protein_Change" = unique(maf_changes_filt$Gene_Protein_Change))
gdsc_prot <- merge(gdsc_all, gdsc_prot_grid, by = "DepMap_ID", all = TRUE)
gdsc_prot <- merge(gdsc_prot, maf_changes_filt, by = c("DepMap_ID", "Gene_Protein_Change"), all = TRUE)
gdsc_prot$Change_Status <- ifelse(!is.na(gdsc_prot$Protein_Change), "Yes", "No")
gdsc_prot$Drug_Gene_Protein_Change <- ifelse(is.na(gdsc_prot$Drug) | is.na(gdsc_prot$Gene_Protein_Change), NA, paste0(gdsc_prot$Drug, "_", gdsc_prot$Gene_Protein_Change))
gdsc_prot$G2P_Drug_Gene_Protein_Change <- ifelse(gdsc_prot$Drug_Gene_Protein_Change %in% unique(as.character(g2p_prot$Drug_Gene_Protein_Change)), "Yes", "No")
gdsc_prot$G2P_Protein_Change <- ifelse(gdsc_prot$Gene_Protein_Change %in% unique(as.character(g2p_prot$Gene_Protein_Change)), "Yes", "No")
gdsc_prot <- merge(gdsc_prot, unique(select(g2p_prot, Drug_Gene_Protein_Change, Direction_Curated)), by = "Drug_Gene_Protein_Change", all.x = TRUE)
gdsc_prot$Database <- "GDSC"
gdsc_prot <- gdsc_prot %>% drop_na(Drug)

@@

```{r merge_crispr_data, eval=FALSE}
crispr_all <- read.delim("./data_munging/19Q2/Achilles_gene_effect_20190514.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
# Remove Entrez gene IDs from colnames
colnames(crispr_all) <- gsub(" .*", "", colnames(crispr_all))
colnames(crispr_all)[1] <- "DepMap_ID"

@@

```{r merge_crispr_fus, eval=FALSE}
fusions_filt <- filter(fusions, FusionPair %in% unique(as.character(g2p_fus$FusionPair)))

@@

```{r merge_crispr_prot, eval=FALSE}
crispr_all <- read.delim("./data_munging/19Q2/Achilles_gene_effect_20190514.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
# Remove Entrez gene IDs from colnames
colnames(crispr_all) <- gsub(" .*", "", colnames(crispr_all))
colnames(crispr_all)[1] <- "DepMap_ID"

@@

    count_n <- dataframe %>% count(Drug, FusionPair, Drug_FusionPair, Fusion_Status) %>% filter(n >= 3)
    count_category <- count_n %>% count(Drug, FusionPair, Drug_FusionPair) %>% filter(n == 2)

@@

>>>>

```{r g2p}
g2p <- read.delim("./data_munging/g2p_db_edited_20190718.csv", sep = ",", header = TRUE, row.names = 1)

@@

g2p$biomarker_type_curated <- ifelse(is.na(g2p$biomarker_type_curated), "None", as.character(g2p$biomarker_type_curated))
g2p_split <- filter(g2p, !is.na(Drug)) %>% group_split(biomarker_type_curated)
g2p_amp <- g2p_split[[1]]
g2p_expr <- g2p_split[[2]]
g2p_fus <- g2p_split[[3]]
g2p_fus$FusionPair <- sapply(X = g2p_fus$Feature.Names, function(x) strsplit(as.character(x)," ")[[1]][1])
g2p_fus$FusionPair <- ifelse(g2p_fus$FusionPair == "Fusions", as.character(g2p_fus$Gene), as.character(g2p_fus$FusionPair))
g2p_fus$FusionPair <- ifelse(g2p_fus$FusionPair == "BCR-ABL", "BCR-ABL1", as.character(g2p_fus$FusionPair))
g2p_fus$Drug_FusionPair <- ifelse(is.na(g2p_fus$Drug) | is.na(g2p_fus$FusionPair), NA, paste0(g2p_fus$Drug, "_", g2p_fus$FusionPair))
g2p_fus$Drug_Fusion_Lineage <- ifelse(is.na(g2p_fus$Drug) | is.na(g2p_fus$FusionPair) | is.na(g2p_fus$disease), NA, paste0(g2p_fus$Drug, "_", g2p_fus$FusionPair, "_", g2p_fus$disease))
g2p_mut <- g2p_split[[4]] %>% drop_na(Direction_Curated)
g2p_mut_genes <- unique(sapply(strsplit(as.character(g2p_mut$Drug_Gene)[!is.na(g2p_mut$Drug_Gene)], "_", fixed = TRUE), function(x) x[2]))

g2p_prot <- unique(filter(g2p, !is.na(Gene_Protein_Change) & !is.na(Drug)) %>% select(disease, Drug, Direction_Curated, Gene, Protein_Change, Gene_Protein_Change))
g2p_prot$Drug_Gene_Protein_Change <- with(g2p_prot, ifelse(is.na(Drug) | is.na(Gene_Protein_Change), NA, paste0(Drug, "_", Gene_Protein_Change)))
g2p_prot$Drug_Gene_Protein_Change_Lineage <- with(g2p_prot, ifelse(is.na(Drug) | is.na(Gene_Protein_Change) | is.na(disease), NA, paste0(Drug, "_", Gene_Protein_Change, "_", disease)))
```

@@

    grid <- expand.grid("Cell_line" = unique(dataframe$Cell_line), "Gene" = gene_list)
    data <-  merge(dataframe, grid, by = "Cell_line", all.y = TRUE)
    print("Merged grid.")
    # Merge metadata
    ## Add columns for G2P drug-gene and drug-gene-lineage sorting
    data$Drug_Gene <- paste0(data$Drug, "_", data$Gene)
    data$G2P_Drug_Gene <- ifelse(data$Drug_Gene %in% g2p_dg, "Yes", "No")
    data$Drug_Gene_Lin <- paste0(data$Drug, "_", data$Gene, "_", data$disease)
    data$G2P_Drug_Gene_Lin <- ifelse(data$Drug_Gene_Lin %in% g2p_dgl, "Yes", "No")
    print("Merged metadata.")
    # Merge mutation calls
    data <- unfactorize(data)
    data <- merge(data, maf_df, by = c("Gene", "DepMap_ID"), all.x = TRUE)
    data$Mutation <- ifelse(is.na(data$Mutation), 0, data$Mutation)
  }
  if(database == "CRISPR") {
    print(paste0("Processing ", database, " data."))
    # Melt CRISPR dataset for merging
    data <- melt(dataframe, id.vars = "DepMap_ID", measure.vars = colnames(crispr_all)[2:ncol(crispr_all)], variable.name = "Gene", value.name = "Score")
    # Merge cell line metadata
    data <- merge(data, ccl_meta, by = "DepMap_ID", all.y = TRUE)
    data$Drug <- "CRISPR"
    data$Drug_Gene <- paste0(data$Drug, "_", data$Gene)
    data$G2P_Drug_Gene <- "No"
    data$Drug_Gene_Lin <- paste0(data$Drug, "_", data$Gene, "_", data$disease)
    data$G2P_Drug_Gene_Lin <- "No"
    print("Merged metadata.")
    # Merge mutation calls
    data <- unfactorize(data)
    data <- merge(data, maf_df, by = c("Gene", "DepMap_ID"), all.x = TRUE)
    data$Mutation <- ifelse(is.na(data$Mutation), 0, data$Mutation)
  }

@@

`r nrow(filter(test, n != 1))`/`r nrow(test)` gene-cell line combinations have more than one mutation in the MAF file. This is corrected in the point mutation filtering done below.
```{r merge_drug_data, eval=TRUE}
ccle_all <- readRDS("./../htscreens_giant_files/pozdeyev_data/pozdeyev2016_ccle_all_edited.rds")
ctrp_all <- readRDS("./../htscreens_giant_files/pozdeyev_data/pozdeyev2016_ctrp_all_edited.rds")
gdsc_all <- readRDS("./../htscreens_giant_files/pozdeyev_data/pozdeyev2016_gdsc_all_edited.rds")

ccle <- MergeOmicsG2P(database = "CCLE", dataframe = ccle_all, maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./data_munging/19Q2/ccle_data_19Q2.rds")
write.csv.gz(ccle %>% drop_na(Score), "./data_munging/19Q2/ccle_data_19Q2.csv.gz")

ctrp <- MergeOmicsG2P(database = "CTRP", dataframe = ctrp_all, maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./../htscreens_giant_files/ctrp_data_19Q2.rds")
write.csv.gz(ctrp %>% drop_na(Score), "./../htscreens_giant_files/ctrp_data_19Q2.csv.gz")

gdsc <- MergeOmicsG2P(database = "GDSC", dataframe = gdsc_all, maf_df = maf_df, ge_df = ge_melt, cn_df = cn_melt, gene_list = g2p_genes, outfile = "./data_munging/19Q2/gdsc_data_19Q2.rds")
write.csv.gz(gdsc %>% drop_na(Score), "./../htscreens_giant_files/gdsc_data_19Q2.csv.gz")
```

@@

ccle_fus_grid <- expand.grid("DepMap_ID" = unique(ccle_all$DepMap_ID), "FusionPair" = unique(fusions_filt$FusionPair))
ccle_fus <- merge(merge(ccle_all, ccle_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "Cell_line", "FusionPair", "disease"), all = TRUE)
ccle_fus$Fusion_Status <- ifelse(!is.na(ccle_fus$LeftGene), "Yes", "No")
ccle_fus$Drug_FusionPair <- with(ccle_fus, ifelse(is.na(Drug) | is.na(FusionPair), NA, paste0(Drug, "_", FusionPair)))
ccle_fus$Drug_Fusion_Lineage <- with(ccle_fus, ifelse(is.na(Drug) | is.na(FusionPair) | is.na(disease), NA, paste0(Drug, "_", FusionPair, "_", disease)))
ccle_fus$G2P_Drug_FusionPair <- ifelse(ccle_fus$Drug_FusionPair %in% unique(as.character(g2p_fus$Drug_FusionPair)), "Yes", "No")
ccle_fus$G2P_Fusion <- ifelse(ccle_fus$FusionPair %in% unique(as.character(g2p_fus$FusionPair)), "Yes", "No")
ccle_fus$G2P_Drug_Fusion_Lineage <- ifelse(ccle_fus$Drug_Fusion_Lineage %in% unique(as.character(g2p_fus$Drug_Fusion_Lineage)), "Yes", "No")
ccle_fus$Database <- "CCLE"

ctrp_fus_grid <- expand.grid("DepMap_ID" = unique(ctrp_all$DepMap_ID), "FusionPair" = unique(fusions_filt$FusionPair))
ctrp_fus <- merge(merge(ctrp_all, ctrp_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "Cell_line", "FusionPair", "disease"), all = TRUE)
ctrp_fus$Fusion_Status <- ifelse(!is.na(ctrp_fus$LeftGene), "Yes", "No")     
ctrp_fus$Drug_FusionPair <- with(ctrp_fus, ifelse(is.na(Drug) | is.na(FusionPair), NA, paste0(Drug, "_", FusionPair)))
ctrp_fus$Drug_Fusion_Lineage <- with(ctrp_fus, ifelse(is.na(Drug) | is.na(FusionPair) | is.na(disease), NA, paste0(Drug, "_", FusionPair, "_", disease)))
ctrp_fus$G2P_Drug_FusionPair <- ifelse(ctrp_fus$Drug_FusionPair %in% unique(as.character(g2p_fus$Drug_FusionPair)), "Yes", "No")
ctrp_fus$G2P_Fusion <- ifelse(ctrp_fus$FusionPair %in% unique(as.character(g2p_fus$FusionPair)), "Yes", "No")
ctrp_fus$G2P_Drug_Fusion_Lineage <- ifelse(ctrp_fus$Drug_Fusion_Lineage %in% unique(as.character(g2p_fus$Drug_Fusion_Lineage)), "Yes", "No")
ctrp_fus$Database <- "CTRP"

gdsc_fus_grid <- expand.grid("DepMap_ID" = unique(gdsc_all$DepMap_ID), "FusionPair" = unique(fusions_filt$FusionPair))
gdsc_fus <- merge(merge(gdsc_all, gdsc_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "Cell_line", "FusionPair", "disease"), all = TRUE)
gdsc_fus$Fusion_Status <- ifelse(!is.na(gdsc_fus$LeftGene), "Yes", "No")
gdsc_fus$Drug_FusionPair <- with(gdsc_fus, ifelse(is.na(Drug) | is.na(FusionPair), NA, paste0(Drug, "_", FusionPair)))
gdsc_fus$Drug_Fusion_Lineage <- with(gdsc_fus, ifelse(is.na(Drug) | is.na(FusionPair) | is.na(disease), NA, paste0(Drug, "_", FusionPair, "_", disease)))
gdsc_fus$G2P_Drug_FusionPair <- ifelse(gdsc_fus$Drug_FusionPair %in% unique(as.character(g2p_fus$Drug_FusionPair)), "Yes", "No")
gdsc_fus$G2P_Fusion <- ifelse(gdsc_fus$FusionPair %in% unique(as.character(g2p_fus$FusionPair)), "Yes", "No")
gdsc_fus$G2P_Drug_Fusion_Lineage <- ifelse(gdsc_fus$Drug_Fusion_Lineage %in% unique(as.character(g2p_fus$Drug_Fusion_Lineage)), "Yes", "No")
gdsc_fus$Database <- "GDSC"

@@

# CCLE
ccle_prot_grid <- expand.grid("DepMap_ID" = unique(ccle_all$DepMap_ID), "Gene_Protein_Change" = unique(maf_changes_filt$Gene_Protein_Change))
ccle_prot <- merge(ccle_all, ccle_prot_grid, by = "DepMap_ID", all = TRUE)
ccle_prot <- merge(ccle_prot, maf_changes_filt, by = c("DepMap_ID", "Gene_Protein_Change"), all = TRUE)
ccle_prot$Change_Status <- ifelse(!is.na(ccle_prot$Protein_Change), "Yes", "No")
ccle_prot$Drug_Gene_Protein_Change <- with(ccle_prot, ifelse(is.na(Drug) | is.na(Gene_Protein_Change), NA, paste0(Drug, "_", Gene_Protein_Change)))
ccle_prot$Drug_Gene_Protein_Change_Lineage <- with(ccle_prot, ifelse(is.na(Drug) | is.na(Gene_Protein_Change) | is.na(disease), NA, paste0(Drug, "_", Gene_Protein_Change, "_", disease)))
ccle_prot$G2P_Drug_Gene_Protein_Change <- ifelse(ccle_prot$Drug_Gene_Protein_Change %in% unique(as.character(g2p_prot$Drug_Gene_Protein_Change)), "Yes", "No")
ccle_prot$G2P_Protein_Change <- ifelse(ccle_prot$Gene_Protein_Change %in% unique(as.character(g2p_prot$Gene_Protein_Change)), "Yes", "No")
ccle_prot$G2P_Drug_Gene_Protein_Change_Lineage <- ifelse(ccle_prot$Drug_Gene_Protein_Change_Lineage %in% unique(as.character(g2p_prot$Drug_Gene_Protein_Change_Lineage)), "Yes", "No")
ccle_prot <- merge(ccle_prot, unique(select(g2p_prot, Drug_Gene_Protein_Change, Direction_Curated)), by = "Drug_Gene_Protein_Change", all.x = TRUE)
ccle_prot$Database <- "CCLE"
ccle_prot <- ccle_prot %>% drop_na(Drug)

# CTRP
ctrp_prot_grid <- expand.grid("DepMap_ID" = unique(ctrp_all$DepMap_ID), "Gene_Protein_Change" = unique(maf_changes_filt$Gene_Protein_Change))
ctrp_prot <- merge(ctrp_all, ctrp_prot_grid, by = "DepMap_ID", all = TRUE)
ctrp_prot <- merge(ctrp_prot, maf_changes_filt, by = c("DepMap_ID", "Gene_Protein_Change"), all = TRUE)
ctrp_prot$Change_Status <- ifelse(!is.na(ctrp_prot$Protein_Change), "Yes", "No")
ctrp_prot$Drug_Gene_Protein_Change <- with(ctrp_prot, ifelse(is.na(Drug) | is.na(Gene_Protein_Change), NA, paste0(Drug, "_", Gene_Protein_Change)))
ctrp_prot$Drug_Gene_Protein_Change_Lineage <- with(ctrp_prot, ifelse(is.na(Drug) | is.na(Gene_Protein_Change) | is.na(disease), NA, paste0(Drug, "_", Gene_Protein_Change, "_", disease)))
ctrp_prot$G2P_Drug_Gene_Protein_Change <- ifelse(ctrp_prot$Drug_Gene_Protein_Change %in% unique(as.character(g2p_prot$Drug_Gene_Protein_Change)), "Yes", "No")
ctrp_prot$G2P_Protein_Change <- ifelse(ctrp_prot$Gene_Protein_Change %in% unique(as.character(g2p_prot$Gene_Protein_Change)), "Yes", "No")
ctrp_prot$G2P_Drug_Gene_Protein_Change_Lineage <- ifelse(ctrp_prot$Drug_Gene_Protein_Change_Lineage %in% unique(as.character(g2p_prot$Drug_Gene_Protein_Change_Lineage)), "Yes", "No")
ctrp_prot <- merge(ctrp_prot, unique(select(g2p_prot, Drug_Gene_Protein_Change, Direction_Curated)), by = "Drug_Gene_Protein_Change", all.x = TRUE)
ctrp_prot$Database <- "CTRP"
ctrp_prot <- ctrp_prot %>% drop_na(Drug)

# GDSC
gdsc_prot_grid <- expand.grid("DepMap_ID" = unique(gdsc_all$DepMap_ID), "Gene_Protein_Change" = unique(maf_changes_filt$Gene_Protein_Change))
gdsc_prot <- merge(gdsc_all, gdsc_prot_grid, by = "DepMap_ID", all = TRUE)
gdsc_prot <- merge(gdsc_prot, maf_changes_filt, by = c("DepMap_ID", "Gene_Protein_Change"), all = TRUE)
gdsc_prot$Change_Status <- ifelse(!is.na(gdsc_prot$Protein_Change), "Yes", "No")
gdsc_prot$Drug_Gene_Protein_Change <- with(gdsc_prot, ifelse(is.na(Drug) | is.na(Gene_Protein_Change), NA, paste0(Drug, "_", Gene_Protein_Change)))
gdsc_prot$Drug_Gene_Protein_Change_Lineage <- with(gdsc_prot, ifelse(is.na(Drug) | is.na(Gene_Protein_Change) | is.na(disease), NA, paste0(Drug, "_", Gene_Protein_Change, "_", disease)))
gdsc_prot$G2P_Drug_Gene_Protein_Change <- ifelse(gdsc_prot$Drug_Gene_Protein_Change %in% unique(as.character(g2p_prot$Drug_Gene_Protein_Change)), "Yes", "No")
gdsc_prot$G2P_Protein_Change <- ifelse(gdsc_prot$Gene_Protein_Change %in% unique(as.character(g2p_prot$Gene_Protein_Change)), "Yes", "No")
gdsc_prot$G2P_Drug_Gene_Protein_Change_Lineage <- ifelse(gdsc_prot$Drug_Gene_Protein_Change_Lineage %in% unique(as.character(g2p_prot$Drug_Gene_Protein_Change_Lineage)), "Yes", "No")
gdsc_prot <- merge(gdsc_prot, unique(select(g2p_prot, Drug_Gene_Protein_Change, Direction_Curated)), by = "Drug_Gene_Protein_Change", all.x = TRUE)
gdsc_prot$Database <- "GDSC"
gdsc_prot <- gdsc_prot %>% drop_na(Drug)

@@

```{r merge_crispr_data, eval=TRUE}
crispr_all <- read.delim("./data_munging/19Q2/Achilles_gene_effect_20190514.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
# Remove Entrez gene IDs from colnames
colnames(crispr_all) <- gsub(" .*", "", colnames(crispr_all))
colnames(crispr_all)[1] <- "DepMap_ID"

@@

```{r merge_crispr_fus, eval=TRUE}
fusions_filt <- filter(fusions, FusionPair %in% unique(as.character(g2p_fus$FusionPair)))
crispr_fus_grid <- expand.grid("DepMap_ID" = unique(crispr$DepMap_ID), "FusionPair" = unique(fusions_filt$FusionPair))
crispr_fus <- merge(merge(crispr, crispr_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "Cell_line", "FusionPair", "disease"), all = TRUE)
crispr_fus$Fusion_Status <- ifelse(!is.na(crispr_fus$LeftGene), "Yes", "No")
crispr_fus$Drug <- "CRISPR"
crispr_fus$Drug_FusionPair <- with(crispr_fus, ifelse(is.na(Drug) | is.na(FusionPair), NA, paste0(Drug, "_", FusionPair)))
crispr_fus$Drug_Fusion_Lineage <- with(crispr_fus, ifelse(is.na(Drug) | is.na(FusionPair) | is.na(disease), NA, paste0(Drug, "_", FusionPair, "_", disease)))
crispr_fus$G2P_Drug_FusionPair <- "No"
crispr_fus$G2P_Fusion <- ifelse(crispr_fus$FusionPair %in% unique(as.character(g2p_fus$FusionPair)), "Yes", "No")
crispr_fus$G2P_Drug_Fusion_Lineage <- "No"
crispr_fus$Database <- "CRISPR"

@@

```{r merge_crispr_prot, eval=TRUE}
crispr_all <- read.delim("./data_munging/19Q2/Achilles_gene_effect_20190514.csv.gz", sep = ",", header = TRUE, check.names = FALSE)
# Remove Entrez gene IDs from colnames
colnames(crispr_all) <- gsub(" .*", "", colnames(crispr_all))
colnames(crispr_all)[1] <- "DepMap_ID"

@@

    count_n <- dataframe %>% count(Drug_FusionPair, Fusion_Status) %>% filter(n >= 3)
    count_category <- count_n %>% count(Drug_FusionPair) %>% filter(n == 2)

@@

  if(tolower(type) == "fusion_lineage") {
    # Require at least 3 samples in each category to run the test, else filter out that Drug_Fusion_Lineage from testing df
    count_n <- dataframe %>% count(Drug_Fusion_Lineage, Fusion_Status) %>% filter(n >= 3)
    count_category <- count_n %>% count(Drug_Fusion_Lineage) %>% filter(n == 2)
    keep <- intersect(count_n$Drug_Fusion_Lineage, count_category$Drug_Fusion_Lineage)
